\begin{multicols}{2}
\section{Song of the Middle-earth Workers}
Words by Christine Davidson.
\\
Tune ’The Lumberjack Song’ by Monty Python.
\\
\\
I’m a hob-b-bit and I’m OK
\\
I drink all night and I eat all day.
\\
He’s a hob-b-bit and he’s OK
\\
He drinks all night and he eats all day.
\\
\\
I sing rude songs, I tell tall tales,
\\
I brush my furry toes,
\\
I like to have communal baths
\\
And take off all my clothes.
\\
\\
I’m a Rider bold and I’m OK
\\
I drink all night and I trot all day.
\\
He’s a Rider bold and he’s OK
\\
He drinks all night and he trots all day.
\\
\\
I like to chase marauding Orcs,
\\
It stops me getting bored.
\\
The girls all love my harness,
\\
I never sheath my sword.
\\
\\
I’m a Dwarf, I am and I’m OK
\\
I delve all night and I forge all day.
\\
He’s a Dwarf, he is and he’s OK
\\
He delves all night and he forges all day.
\\
\\
I mine for gold and precious jewels,
\\
My mattress for to stuff.
\\
No lady Dwarf will have me,
\\
I just can’t get enough.
\\
\\
\\
\\
\\
\\
\\
I’m an Elf, I am, and I’m OK
\\
I feast all night and I run all day.
\\
He’s an Elf, he is, and he’s OK
\\
He feasts all night and he runs all day.
\\
\\
I dance with grace, I also sing,
\\
My voice is rather high.
\\
I always hunt the noble stag,
\\
I’m sure you can guess why.
\\
\\
I’m a Ranger bold, and I’m OK
\\
I track all night and I fight all day.
\\
He’s a Ranger bold, and he’s OK
\\
he tracks all night and he fights all day.
\\
\\
I roam the Wilds to keep folk safe,
\\
A lonely life, its true.
\\
But when my camp-fire’s burning,
\\
I know just what to do.
\\
\\
I’m a Naz-a-g\^ul and I’m OK
\\
I’m high all night and I hiss all day.
\\
He’s a Naz-a-g\^ul and he’s OK
\\
He’s high all night and he hisses all day.
\\
\\
I wear a ring, and long black robes,
\\
I love inflicting pain.
\\
There’s nine of us, we all take turns,
\\
It’s cut and come again.

\end{multicols}
